### 2015-03-24 manuscript/AppendixA.tex
SpatPred draft to Peter and Devin for first time - doesn't have Steller example integrated into text yet
Cleaned up and compiled R package.  Added gIVH function that computes gIVH for a generic model using same procedure used in analysis.  Manuscript is as initially submitted to Ecology, March 2015

\begin{center}
Appendix A: Model formulation and Gibbs sampling algorithms for certain classes and extensions of the generalized linear model
\bigskip
\end{center}
\vspace{.3in}

@@

\section{Models}
\subsection{Generalized linear models (GLM)}

@@

\subsection{Generalized additive models (GAM)}

@@

\hspace{.5in}There are a number of ways smooth relationships can be modeled; in order to formulate a GAM in the notation of Eq. \ref{eq:basic_model} we employ a knot-based kernel smoother with a Gaussian radial basis function.  The basic notion is to place $k_j$ knots, which we will denote by $\boldsymbol{\omega}_j = \{ \omega_{1j},\omega_{2j},\hdots,\omega_{k_j j} \}$, throughout the range of a given regressor $j$, where the number of knots controls the level of smoothing.  For each regressor of interest, we can then calculate a matrix ${\bf K}_j$ of dimension $(n,k_j)$, with entries $\mathcal{N}(X_{ij};\omega_j,\tau_{\omega,j})$, where $\mathcal{N}(x;\mu,\tau)$ denotes a Gaussian distribution with mean $\mu$ and precision $\tau$.  We can then introduce additional regression coefficients $\boldsymbol{\alpha}_j$ to help model the smooth relationship, and incorporate these into the linear predictor.  In the case of one smooth term, we then have  in Eq. \ref{eq:basic_model}:
\begin{linenomath*}
\begin{equation}
  \label{eq:GAM}
  \boldsymbol{\xi}={\bf X} \boldsymbol{\beta} + {\bf K}_j \boldsymbol{\alpha}_j
\end{equation}
\end{linenomath*}
When fitting such a model, one needs to select the number and location of knots, as well as the precision parameter $\tau_{\omega,j}$ for the Gaussian basis kernels.  This could be done using some notion of optimality or prediction error (as with cross validation).  In practice, a simple recommendation is to set $\tau_{\omega,j}$ less than the range of the modeled covariate, and greater than the typical difference between observed values of the covariate.

@@

There are a variety of ways spatial autocorrelation can be included in regression models, depending on (i) the spatial support (i.e., continuous vs. discrete), and (ii) the particular mechanism used to impart correlation.  Here, we shall focus on areal models for discrete spatial support, as our impression is that these are more commonly employed in ecological studies.  Such models require that data are aggregated at the level of some sample unit (plots, grid cells, etc.).  Spatio-temporal regression models (STRMs) for areal data are often specified in a similar fashion to GLMs and GAMs:
\begin{linenomath*}
\begin{equation}
  \label{eq:spat_reg}
  \boldsymbol{\xi}={\bf X} \boldsymbol{\beta} + \boldsymbol{\eta},
\end{equation}
\end{linenomath*}
where $\boldsymbol{\eta}$ represent spatially autocorrelated effects.  In this treatment we shall consider two approaches for
inducing spatial autocorrelation in $\boldsymbol{\eta}$: process convolution
\citep[PC;][]{Higdon1998} and restricted spatial regression \citep[RSR;][]{Reich2006,Hodges2010,Hughes2013}.

The PC implementation works by placing $k$ knots throughout the spatial domain being analyzed, and like our GAM formulation, uses distances from the center point of each sample unit to each of these knot locations to induce spatial structure.  Using similar notation to our GAM formulation, we denote these knots as $\boldsymbol{\omega} = \{ \boldsymbol{\omega_{1}},\boldsymbol{\omega}_{2},\hdots,\boldsymbol{\omega}_{k} \}$; the $\boldsymbol{\omega}_m$ are bivariate in this  instance as space is assumed to be two dimensional.  We then construct a matrix ${\bf K}$ of dimension $(n,k)$ with entries $\mathcal{BVN}({\bf s}_i;\boldsymbol{\omega}_m,\tau_{\omega})$, where $\mathcal{BVN}({\bf x};{\bf \mu},\tau)$ denotes a bivariate Gaussian distribution with mean $\boldsymbol{\mu}$ and precision $\tau$.  As with our GAM model we introduce additional regression coefficients $\boldsymbol{\alpha}$ to estimate the level of spatial smoothing conditional on the assumed knot structure and reparameterize the STRM as
\begin{linenomath*}
\begin{equation}
  \label{eq:PC}
  \boldsymbol{\xi}={\bf X} \boldsymbol{\beta} + {\bf K} \boldsymbol{\alpha}
\end{equation}
\end{linenomath*}
This model is structurally very similar to the GAM model (indeed it may be interpreted as a GAM with a bivariate smooth on spatial location).  Similarly, we can rearrange terms to write it similar to the GLM, such that
$\boldsymbol{\xi}={\bf X}_{aug} \boldsymbol{\beta}_{aug}$,
where in this case ${\bf X}_{aug} = \left[ {\bf X} \hspace{3mm} {\bf K} \right]$, and $\boldsymbol{\beta}_{aug}=\left[  \boldsymbol{\beta} \hspace{3mm} \boldsymbol{\alpha} \right] ^\prime$.

The RSR approach to spatial regression uses a reduced-rank version of the popular intrinsic conditionally autoregressive \citep[ICAR;][]{Besag1995,Rue2005} model for spatial random effects, reparameterized so that basis vectors are orthogonal to the main effects of interest.  This approach has generated substantial recent interest, as fixed effects retain primacy in explaining variation in the ecological process of interest and problems with spatial confounding between fixed and random effects are eliminated. As such, spatial random effects are only used to account for residual autocorrelation \citep{Reich2006,Hodges2010} and the decision to incorporate spatial autocorrelation has little effect on the point estimates of fixed effects.  In addition, reduced dimension spatial models such as RSR lighten computational burden while still accounting for course-scale spatial autocorrelation \citep[see e.g.][]{LatimerEtAl2009,Wikle2010,Hughes2013}.  It turns out that RSR models can also be written in the form of Eq. \ref{eq:PC}, using a
different choice of ${\bf K}$ \citep{Hughes2013}, constructed as follows:
\begin{enumerate}
  \item Define the residual projection matrix ${\bf P}^\perp={\bf I}-{\bf X}({\bf X}^\prime{\bf X})^{-1}{\bf X}^\prime$
  \item Calculate the Moran operator matrix $\boldsymbol{\Omega}=J{\bf P}^\perp \mathcal{W}{\bf P}^\perp/{\bf 1}^\prime \mathcal{W} {\bf 1}$
  \item Define ${\bf K}$ as an $(n \times m)$ matrix, where the columns of ${\bf K}$ are composed of the eigenvectors  associated with the largest $m$ eigenvalues of $\boldsymbol{\Omega}$. Hughes and Haran (\citeyear{Hughes2013}) used simulation to explore a range of such values and concluded $m=50-100$ should suffice for most applications.
\end{enumerate}
Here, ${\bf I}$ an identity matrix, ${\bf 1}$ is a column vector of ones, and $\mathcal{W}$ represents an association matrix describing the spatial neighborhood structure of sampling units.  For instance, for a first order neighborhood structure, $\mathcal{W}$ would include a 1 for all rows $i$ and columns $j$ where sampling unit $i$ and $j$ are neighbors \citep[see][for alternative association matrices]{Rue2005}.

@@

Setting the prior for the suite of regression parameters as $[\boldsymbol{\beta}] = \textrm{MVN}({\bf 0},(\tau_\beta X^\prime X)^{-1})$ results in the full conditional distribution
\begin{linenomath*}
\begin{equation*}
   [\boldsymbol{\beta} | \cdot] \equiv \mathcal{N}(({\bf X}^\prime {\bf X})^{-1}{\bf X}^\prime \boldsymbol{\mu},({\bf X}^\prime {\bf X})^{-1} (\tau_\epsilon + \tau_\beta)^{-1}).
\end{equation*}
\end{linenomath*}
We set $\tau_\beta = 0.01$ for applications described in this paper.

@@

\subsection{Gibbs sampler for the PC STRM model}

The Gibbs sampler for the process convolution version of the STRM model consists of the following:

@@

We impose the same Gaussian prior on smoothing kernel weights, $\boldsymbol{\alpha} \sim \mathcal{N}(0,\tau_\alpha^{-1})$ as for the GAM.  The resulting full conditional is simply
\begin{linenomath*}
\begin{equation*}
   [\boldsymbol{\alpha} | \cdot] \equiv \mathcal{MVN}(({\bf K}^\prime {\bf K})^{-1}{\bf K}^\prime (\boldsymbol{\mu}-{\bf X}\boldsymbol{\beta}),({\bf K}^\prime {\bf K}^{-1} (\tau_\epsilon + \tau_\alpha)^{-1}).
\end{equation*}
\end{linenomath*}

\subsection{Gibbs sampler for the RSR STRM model}

Although ${\bf K}$ is defined differently in the RSR model, the Gibbs sampler remains the same as for the the PC model, with the exception of a modified full conditional for $[\boldsymbol{\alpha}|\cdot]$ owing to a different prior specification for $\boldsymbol{\alpha}$.  We must also update an additional precision parameter associated with spatial random effects, $\tau_\eta$.

In the RSR model, the implied prior for reduced dimension spatial effects is $\boldsymbol{\alpha} \sim \text{MVN}(0,\tau_\eta^{-1}{\bf K}^\prime {\bf Q} {\bf K})$.  The resulting full conditional is
\begin{linenomath*}
\begin{eqnarray*}
   [\boldsymbol{\alpha} | \cdot] & = & \mathcal{MVN}({\bf M},\boldsymbol{\Sigma}), \text{ where} \\
   \boldsymbol{\Sigma}^{-1} & = & {\bf K}^\prime {\bf K}\tau_\epsilon+\tau_\eta{\bf K}^\prime {\bf Q} {\bf K} \text{ and} \\
    {\bf M} & = & \boldsymbol{\Sigma} \tau_\epsilon {\bf K}^\prime (\boldsymbol{\mu} - {\bf X} \boldsymbol{\beta}).
\end{eqnarray*}
\end{linenomath*}
See for example, \citet{ConnEtAl2014}.

@@

>>>>

\begin{center}
Appendix A: Model formulation, Gibbs sampling algorithms, and gIVH calculations for certain classes and extensions of the generalized linear model
\bigskip
\end{center}
\vspace{.3in}

@@

\section{Models}
\subsection{Generalized linear models (GLMs)}

@@

\subsection{Generalized additive models (GAMs)}

@@

\hspace{.5in}There are a number of ways smooth relationships can be modeled; in order to formulate a GAM in the notation of Eq. \ref{eq:basic_model} we employ a knot-based kernel smoother with a Gaussian radial basis function.  The basic notion is to place $k_j$ knots, which we will denote by $\boldsymbol{\omega}_j = \{ \omega_{1j},\omega_{2j},\hdots,\omega_{k_j j} \}$, throughout the range of a given regressor $j$, where the number of knots controls the level of smoothing.  For each regressor of interest, we can then calculate a matrix ${\bf K}_j$ of dimension $(n,k_j)$ (where $n$ gives the number of observed data locations), with entries $z_{ik}=\mathcal{N}(X_{ij};\omega_{kj},\tau_j)$, where $\mathcal{N}(x;\mu,\tau)$ denotes a Gaussian distribution with mean $\mu$ and precision $\tau$, $i$ indexes a particular observed data location, and $k$ denotes the $k$th knot for covariate $j$, $k \in \{1,2,\hdots,k_j \}$. We can then introduce additional regression coefficients $\boldsymbol{\alpha}_j$ to help model the smooth relationship, and incorporate these into the linear predictor.  In the case of one smooth term, we then have  in Eq. \ref{eq:basic_model}:
\begin{linenomath*}
\begin{equation}
  \label{eq:GAM}
  \boldsymbol{\xi}={\bf X} \boldsymbol{\beta} + {\bf K}_j \boldsymbol{\alpha}_j
\end{equation}
\end{linenomath*}
When fitting such a model, one needs to select the number and location of knots, as well as the precision parameter $\tau_{\omega,j}$ for the Gaussian basis kernels.  This could be done using some notion of optimality or prediction error (as with cross validation).  In practice, a simple recommendation is to set $\tau_{\omega,j}$ less than the range of the modeled covariate, and greater than the typical difference between observed values of the covariate.

@@

\hspace{.5in}There are a variety of ways spatial autocorrelation can be included in regression models, depending on (i) the spatial support (i.e., continuous vs. discrete), and (ii) the particular mechanism used to impart correlation.  Here, we shall focus on areal models for discrete spatial support, as our impression is that these are more commonly employed in ecological studies.  Such models require that data are aggregated at the level of some sample unit (plots, grid cells, etc.).  Spatio-temporal regression models (STRMs) for areal data are often specified in a similar fashion to GLMs and GAMs:
\begin{linenomath*}
\begin{equation}
  \label{eq:spat_reg}
  \boldsymbol{\xi}={\bf X} \boldsymbol{\beta} + \boldsymbol{\eta},
\end{equation}
\end{linenomath*}
where $\boldsymbol{\eta}$ represent spatially autocorrelated effects.  In this treatment we shall limit consideration one approach for
inducing spatial autocorrelation in $\boldsymbol{\eta}$: restricted spatial regression \citep[RSR;][]{Reich2006,Hodges2010,Hughes2013}.

\hspace{.5in}The RSR approach to spatial regression uses a reduced-rank version of the popular intrinsic conditionally autoregressive \citep[ICAR;][]{Besag1995,RueHeld2005} model for spatial random effects, reparameterized so that basis vectors are orthogonal to the main effects of interest.  This approach has generated substantial recent interest, as fixed effects retain primacy in explaining variation in the ecological process of interest and problems with spatial confounding between fixed and random effects are eliminated. As such, spatial random effects are only used to account for residual autocorrelation \citep{Reich2006,Hodges2010} and the decision to incorporate spatial autocorrelation has little effect on the point estimates of fixed effects.  In addition, reduced dimension spatial models such as RSR lighten computational burden while still accounting for course-scale spatial autocorrelation \citep[see e.g.][]{LatimerEtAl2009,Wikle2010,Hughes2013}.  It turns out that RSR models can also be written in the form of Eq. \ref{eq:PC}, using a
different choice of ${\bf K}$ \citep{Hughes2013}, constructed as follows:
\begin{enumerate}
  \item Define the residual projection matrix ${\bf P}^\perp={\bf I}-{\bf X}({\bf X}^\prime{\bf X})^{-1}{\bf X}^\prime$
  \item Calculate the Moran operator matrix $\boldsymbol{\Omega}=J{\bf P}^\perp {\bf W}{\bf P}^\perp/{\bf 1}^\prime {\bf W} {\bf 1}$, where $J$ is the number of areal survey units
  \item Define ${\bf K}$ as an $(n \times m)$ matrix, where the columns of ${\bf K}$ are composed of the eigenvectors  associated with the largest $m$ eigenvalues of $\boldsymbol{\Omega}$. Hughes and Haran (\citeyear{Hughes2013}) used simulation to explore a range of such values and concluded $m=50-100$ should suffice for most applications.
\end{enumerate}
Here, ${\bf I}$ an identity matrix, ${\bf 1}$ is a column vector of ones, and ${\bf W}$ represents an association matrix describing the spatial neighborhood structure of sampling units.  For instance, for a first order neighborhood structure, ${\bf W}$ would include a 1 for all rows $i$ and columns $j$ where sampling unit $i$ and $j$ are neighbors \citep[see][for alternative association matrices]{RueHeld2005}.

@@

Setting the prior for the suite of regression parameters as $[\boldsymbol{\beta}] = \mathcal{MVN}({\bf 0},(\tau_\beta X^\prime X)^{-1})$ results in the full conditional distribution
\begin{linenomath*}
\begin{equation*}
   [\boldsymbol{\beta} | \cdot] \equiv \mathcal{N}(({\bf X}^\prime {\bf X})^{-1}{\bf X}^\prime \boldsymbol{\mu},({\bf X}^\prime {\bf X})^{-1} (\tau_\epsilon + \tau_\beta)^{-1}).
\end{equation*}
\end{linenomath*}
We set $\tau_\beta = 0.01$ for applications described in this paper.

@@

\subsection{Gibbs sampler for the STRM model}

The Gibbs sampler for the RSR version of the STRM model consists of the following:

@@

In the RSR model, the implied prior for reduced dimension spatial effects is $\boldsymbol{\alpha} \sim \mathcal{MVN}(0,\tau_\eta^{-1}{\bf K}^\prime {\bf Q} {\bf K})$.  The resulting full conditional is
\begin{linenomath*}
\begin{eqnarray*}
   [\boldsymbol{\alpha} | \cdot] & = & \mathcal{MVN}({\bf M},\boldsymbol{\Sigma}), \text{ where} \\
   \boldsymbol{\Sigma}^{-1} & = & {\bf K}^\prime {\bf K}\tau_\epsilon+\tau_\eta{\bf K}^\prime {\bf Q} {\bf K} \text{ and} \\
    {\bf M} & = & \boldsymbol{\Sigma} \tau_\epsilon {\bf K}^\prime (\boldsymbol{\mu} - {\bf X} \boldsymbol{\beta}).
\end{eqnarray*}
\end{linenomath*}
See for example, \citet{ConnEtAl2014}.

@@

\subsection{Calculating the gIVH}

In order to calculate prediction variance on the real scale for generalized models, it is necessary to use a procedure such as the delta method \citep{Dorfman1938}.  In particular, we can write the variance of the Poisson expectation as
\begin{linenomath*}
\begin{eqnarray}
  \label{eq:var-lambda}
  {\rm var}(\boldsymbol{\lambda}_x) & = & {\rm var}(g(\boldsymbol{\mu}_x)) \\
  & \approx & \boldsymbol{\Delta} {\rm var}(\boldsymbol{\mu}_x)\boldsymbol{\Delta}^\prime,
%  \boldsymbol{\Delta} & = & \left[ \begin{array}{cccc}
%      \frac{\partial g(\mu_1)}{\partial \mu_1} & \frac{\partial g(\mu_1)}{\partial \mu_2} & %\hdots & \frac{\partial g(\mu_1)}{\partial \mu_n} \\
%      \frac{\partial g(\mu_2)}{\partial \mu_1} & \frac{\partial g(\mu_2)}{\partial \mu_2} & %\hdots & \frac{\partial g(\mu_2)}{\partial \mu_n} \\
%      \vdots & \vdots & \ddots & \vdots \\
%      \frac{\partial g(\mu_n)}{\partial \mu_1} & \frac{\partial g(\mu_n)}{\partial \mu_2} & %\hdots & \frac{\partial g(\mu_n)}{\partial \mu_n} \\
%  \end{array} \right].
\end{eqnarray}
\end{linenomath*}
where $\boldsymbol{\Delta}$ is a matrix of partial derivatives $\partial g(\mu_r)/\partial \mu_c$ ($r$ and $c$ denoting rows and columns of $\boldsymbol{\Delta}$, respectively).  Under common univariate link functions (e.g. log, logit, probit), $\boldsymbol{\Delta}$ has a diagonal form, while for multivariate links (e.g. multinomial logit) $\boldsymbol{\Delta}$ will be dense.

\hspace{.5in} Unlike Cook's original formulation, the gIVH will often involve unknown parameters.  Further, the exact form of ${\rm var}(\hat{\boldsymbol{\beta}}_{aug})$ depends on the underlying model structure and estimation procedure.  We impose a probability distribution $[\boldsymbol{\theta}]$ for unknown parameters, and compute prediction variance as
\begin{linenomath*}
\begin{equation}
  \label{eq:E_var_lambda}
  {\rm var}(\boldsymbol{\lambda}_x | {\bf Y}) = \int_{\boldsymbol{\theta}} {\rm var}(\boldsymbol{\lambda}_x | {\bf Y}, \boldsymbol{\theta}) [\boldsymbol{\theta}] d \boldsymbol{\theta}.
\end{equation}
\end{linenomath*}

\hspace{.5in} Our approach in this paper is to conduct a Bayesian analysis (using the Gibbs sampling algorithms outlined above) and substitute the posterior distribution $[\boldsymbol{\theta}|{\bf Y}]$ for $[\boldsymbol{\theta}]$ in Eq. \ref{eq:E_var_lambda}. Under this approach, one simply sets ${\rm Var}(\mu_x)$ equal to the posterior variance of $\mu_x$ (across Markov chain iterations).  In the case of the log link function, one also needs an estimate for $\mu_x$ to use in delta method calculations; we used the posterior median for each sampling unit.  Although we use a Bayesian formulation for modeling convenience, one could also consider substituting parametric approximations for ${\rm Var}(\mu_x)$ and $\mu_x$ based on output from standard likelihood-based analyses.

### 2015-03-24 manuscript/AppendixB.tex
Cleaned up and compiled R package.  Added gIVH function that computes gIVH for a generic model using same procedure used in analysis.  Manuscript is as initially submitted to Ecology, March 2015

Spatially explicit statistical models are increasingly used to estimate animal abundance and predict species distributions from count data.  We employed a simulation study to examine the ability of the generalized independent variable hull (gIVH) to diagnose potential areas across the landscape where predictions of animal abundance using these models may be problematic, and to determine whether statistical inferences are more robust when restricted to sampling units within the gIVH.  Each simulation replicate consisted of several steps, including
\begin{enumerate}
  \item Simulate three hypothetical, statistically dependent, spatially autocorrelated environmental covariates over a 30 by 30 grid,
  \item Simulate animal abundance across the landscape as a function of environmental covariates,
  \item Simulate animal population surveys across the landscape, including the position of count quadrats and the resulting animal counts,
  \item Estimate animal abundance as a function of two of the environmental covariates according three different models: a generalized linear model (GLM), a generalized additive model (GAM), and a spatio-temporal regression model (STRM).  For the latter, only a spatial dimension was modeled.  All such models were specified hierarchically, with MCMC used for posterior simulation.
  \item Calculate the gIVH using realized posterior variance (i.e. after data were collected and analyzed).
\end{enumerate}
We now describe each of these tasks and results of the simulation study in further detail.  All analyses were performed in the R programming environment \citep{RTeam2012}; requisite code to recreate analyses is available in the R package \texttt{SpatPred} that accompanies this article.

@@

@@

@@

>>>>

Spatially explicit statistical models are increasingly used to estimate animal abundance and predict species distributions from count data.  We employed a simulation study to examine the ability of the generalized independent variable hull (gIVH) to diagnose potential areas across the landscape where predictions of animal abundance using these models may be problematic, and to determine whether statistical inferences are more robust when restricted to sampling units within the gIVH.  Each simulation replicate consisted of several steps (Fig. \ref{}), including
\begin{enumerate}
  \item Simulate three hypothetical, statistically dependent, spatially autocorrelated environmental covariates over a 30 by 30 grid,
  \item Simulate animal abundance across the landscape as a function of environmental covariates,
  \item Simulate animal population surveys across the landscape, including the position of count quadrats and the resulting animal counts,
  \item Estimate animal abundance as a function of two of the environmental covariates according three different models: a generalized linear model (GLM), a generalized additive model (GAM), and a spatio-temporal regression model (STRM).  For the latter, only a spatial dimension was modeled.  All such models were specified hierarchically, with MCMC used for posterior simulation.
  \item Calculate the gIVH using realized posterior variance (i.e. after data were collected and analyzed).
\end{enumerate}
We now describe each of these tasks and results of the simulation study in further detail before describing results.  All analyses were performed in the R programming environment \citep{RTeam2012}; requisite code to recreate analyses is available in the R package \texttt{SpatPred} that accompanies this article.

@@

As suggested in Appendix A, we used Eq. A.7 to calculate the gIVH, substituting in samples from the joint posterior distribution of each model for $\boldsymbol{\theta}$.

\centerline{\sc Results}

Posterior predictions from simulations indicated that the distribution for proportional error in total abundance was right skewed when statistical inference was made with regard to the entire survey area (Fig. \ref{fig:sim_boxplots}).  This was particularly true for GLM and STRM models, and was exacerbated when convenience sampling was employed.  The magnitude of mean absolute bias was reduced when inference was constrained to the gIVH for all 6 configurations of survey design and estimation model.  Interestingly, the convolution kernel GAMs we employed often underestimated total abundance, perhaps because of dampening ``edge effects" at extreme ranges of observed covariates, or possibly because interactions among covariates were not modeled.  For GLMs and STRMs, positive proportional bias was the rule, and was of concerning magnitude (e.g. $\approx 0.3$; Fig. \ref{fig:sim_boxplots}) for GLMs and STRMs when convenience sampling was employed and inference was not restricted to the gIVH.

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=6in]{sim_maps.pdf}
\end{center}
\caption{Depiction of a single simulation scenario.  Panels (A-C) give simulated covariate values, panel D gives true animal abundance, (E) gives estimated abundance from a GLM run on count data from a spatially balanced survey design, and (F) gives abundance from a GLM applied to count data from a convenience survey.  In (E-F), predictions outside the gIVH are represented by black boxes, and sampling locations are represented with an x.  For the convenience sample, the median posterior abundance prediction for the entire survey area is $57\%$ greater than true abundance when inference is made to the whole study area.  When inference is limited to the gIVH, median posterior abundance was just $16\%$ greater than true abundance.}
\label{fig:sim_maps}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=6in]{bias_generic.pdf}
\end{center}
\caption{Boxplots summarizing distribution of proportional error in the posterior predictive median of abundance for the simulation study as a function of estimation model (x-axis), survey design (columns) and whether or not inference was restricted to the gIVH (rows).  The lower and upper limits of each box correspond to first and third quartiles, while whiskers extend to the lowest and highest observed bias within 1.5 interquartile range units from the box.  Outliers outside of this range are denoted with points.  Horizontal lines within boxes denote median bias.  The two numbers located below each boxplot indicate mean bias (upper number) and the number of additional outliers for which proportional bias was greater than 2.0 (lower number). }
\label{fig:sim_boxplots}
\end{figure}
